Processing of visual and non-visual naturalistic spatial information in the "parahippocampal place area"

### 2021-01-26 paper/main.tex
discussion of prim. contrasts (AD & AV; group)

\begin{table*}[h!]
\caption{Significant clusters (z-threshold Z>3.4; p<.05 cluster-corrected)
    of the primary $t$-contrast for the audio-visual movie comparing cuts to a
    setting that was not depicted before to a recurring setting
    (\texttt{vse\_new > vpe\_old}).
    Clusters sorted by voxel size.
    The first brain structure given contains the voxel with the maximum Z-Value,
    followed by brain structures from posterior to anterior, and partially
    covered areas (l. = left; r. = right; c. = cortex; g. = gyrus).}
\label{tab:res-av-group1}
\begin{tabular}{rrrrrrrrrp{3cm}}
\toprule
& & & \multicolumn{3}{r}{max location (MNI)} & \multicolumn{3}{r}{center of gravity (MNI)} &
\\ \cmidrule{4-6} \cmidrule{7-9}
voxels & $p_{corr.}$ & Z-max & x & y & z  & x & y & z & structure \\
\midrule
3003 & 0 & 5.31 & 22.5 & -45.5 & -12 & 4.53 & -63.3 & -3.72 & r. lingual g.; r. cuneal c., intracalcarine c., bilaterally occipital fusiform g., temporal fusiform c., posterior parahippocampal c.  \\
154 & 0.000000656 & 4.46 & -35 & -83 & 28 & -32.8 & -86.2 & 21.4 & l. superior lateral occipital c. \\
121 & 0.00000769 & 4.65 & 25 & -80.5 & 25.5 & 23.7 & -83.8 & 25.4 & r. superior lateral occipital cortex \\
\bottomrule
\end{tabular}
\end{table*}

@@

\todo[inline]{if we report procedure of Sengupta as detailed as it is now in the
following paragraph (imo it's too long), we probably need to explain the
differences between strict, relaxed, simple set in more detail in the method
section}
% Sengupta et al., 2016
The visual localizer experiment \citep{sengupta2016extension} yielded bilateral
[parahippocampal] clusters in 12 of 14 subjects and an unilateral right clusters
in two subjects (sub-04, sub-20).
% Sengupta: 1 of 3
Individual PPAs were assessed by visually inspecting thresholded $z$-maps
(Z>1.64, p<.05 cluster corrected) of three different $t$-contrasts
(\textit{strict}, \textit{relaxed}, and \textit{simple} stimulus set, cf.
\citep{sengupta2016extension}).
% procedure a)
Starting with the most conservative contrast (\textit{strict} set) and a
threshold of t = 2.5, we looked for clusters with at least 20 voxels (using
AFNI).
% procedure b)
We titrated [?] the threshold in the range of [2, 3] until we found an isolated
cluster for the PPA.
% Sengupta: procedure b)
If a cluster was not found or not isolated, we used a contrast from the
\textit{relaxed} set, or finally the \textit{simple} set\todo{not used for PPA},
and repeated the process until we found a cluster that matched the expected
anatomical location based on literature \citep{epstein1998ppa}.

@@

\todo[inline]{BA-plots only shortly mentioned now}
% Bland-Altman-Plots
To better depict the agreement and difference between the results of the visual
localizer and the primary AD contrast, we created a Bland-Altman-Plot for every
subject (see Figure \ref{fig:bland-altman}).
% what it depicts
Each subplot visualizes the mean value and difference (localizer minus AD) of
two spatially corresponding voxels in the unthresholded $z$-maps.
% top KDE plot
A shift of the distribution to voxels with a mean above zero can be seen the
further we constrain voxels to the individual PPA (see KDE plot for the x-axis).
% right KDE plot
Values above the horizontal line depict voxels that show a higher $z$-value in
the dedicated localizer, values below the horizontal line depict voxels that
show higher $z$-value in the AD stimulus.

@@

% previous studies
Previous studies reported bilaterally increased hemodynamic activity in the PPA
when participants were watching static pictures of landscape compared to
pictures of faces or objects (e.g. \citep{epstein1998ppa,
epstein1999parahippocampal}) whereas one study using spoken sentences reported
mixed results \citep{aziz2008modulation}.
% current study: similar
In line with previous studies, we use here also operationalize spatial
perception via general linear model (GLM) $t$-contrasts.
% current study: dissimilar
Contrary to previous studies, our current operationalization is not based on
carefully designed sets of stimuli but based on annotated stimulus features
incidentially occurring in an audio-visual movie and its audio-description.
% group AV
On a group level, whole brain-analysis results for the movie stimulus show
signifcantly increased hemodynamic activity spatially overlapping with a
traditionally localized PPA but also extending into earlier visual cortices.
% group AD
Results for the audio-description stimulus reveal significant activation
restricted to the anterior part of the PPA.
% individual level
On an individual level, results of the audio-description show significant
bilateral clusters in the anterior PPA of nine subjects and significant
unilateral clusters in two subjects.
% meaning 1
Results suggest that increased activation in the PPA during the perception of
static pictures generalizes to the perception of spatial information embedded in
a movie and an exclusively auditory stimulus.
% meaning 2
Our results provide further evidence that the PPA can be divided into functional
subregions. An auditory narrative might substitute a visual paradigm to localize
the PPAs anterior part in visually impaired subjects.

@@

\todo[inline]{AV is "intermediate step": natural but still visual; similar:
\citep{bartels2004mapping, hasson2004intersubject} (mention here already or at
the end of topic)}

% AV stimulus
Group results of the AV stimulus' primary contrast yielded bilateral clusters
that span the group overlap of individual PPA ROIs from anterior to posterior.
% difference in location/size to AD and VIS
Clusters also expand into more posterior regions (occipital fusiform gyrus,
lingual gyrus, and intracalcarine cortex).\todo{which of these regions do (not)
overlap with group ROI?}

\todo[inline]{bigger size of clusters is not surprising; imo still impressive
low amount of random clusters in the brain)}

% confound of higher perception
This larger extension, especially into the primary visual cortex, can be
attributed to the fact that we averaged the content of individual frames after a
cut and did not control for confounding features like depicted faces or objects
or attentional focus of subjects.
% shortcomings
m.a.W.: Results of the AV stimulus that we ran as a conceptual control are
tempered by using different kind of movie cuts regardless of the visual content
of the movie frame after the respective cuts.
% which leads to the ``blurred'' results

\todo[inline]{we exploit a confound induced by cinematography; field size
decreases later in the movie; this is a confound based on cinematography => the
stimulus changes over time; (ergo: man sollte sich bißchen mit Cinematographie
auskennen und/oder stimulus annotation in model nehmen, wenn man was mit movies
machen will)}

% summary: nevertheless
\todo[inline]{Nevertheless, group results from analysis using more natural
visual stimulation suggest that... (cf. \citep{bartels2004mapping,
hasson2004intersubject})}

\todo[inline]{approach of contrasting cuts was adventorous, annotation of speech
suited better in the first place, and the auditory thing ist more interesting
anyway, we did not aim for a substition of classic localizer via movie; but if
you wanna do it, you should...:}

Since the capability to isolate clusters or networks correlating with specific
perceptual (or cognitive) processes is influenced by the amount of annotated
stimulus features further studies focusing on visual perception should annotate
and model visual features of naturalistic stimuli more rigorously.
% solution
Future studies that aim to use a movie to localize different visual areas should
extensively annotate the content of frames (e.g. using the open-source solution
``Pliers'' for feature extraction from a visual naturalistic stimulus;
\citep{mcnamara2017developing}) and record the subject's visual attention via
eye-tracking.

@@

\todo[inline]{since the picture of PPA is far more unclear in auditory
domain and we have a pretty nice stimulus with a narrator and a
pretty nice annotation, we focussed on the audio-description}

@@

% AD stimulus
Group results of the AD stimulus' primary contrast yielded spatially concise
clusters in the anterior part of the PPA group overlap that we gained from a
visual localizer experiment \citep{sengupta2016extension}.
% diff to Aziz (2008)
Unlike \citep{aziz2008modulation} who modeled events from on- to offset of
sentences (describing unknown and famous places and faces), we modeled events
from on- to offset of single words (that indicats the visual content to the
listener).
% conclusion
\citep{aziz2008modulation} found significantly increased activity in only the
left PPA and only for sentences describing famous places compared to famous
faces. Contrary, our group results suggest that auditory spatial information
compared to non-spatial information correlates with bilaterally increased
activation in its anterior.\todo{nice! and\dots?}

% tasks in previous studies
Usually studies that use small sets of experimentally controlled stimuli also
employ a task to keep subjects attentive to the stimuli.
% but epstein1998
Nevertheless, one early block-design study \citep{epstein1998ppa} compared
results from a paradigm that employed a (perceptual) judgment task of static
pictures to the same paradigm but without that task.
% results during no task
Hemodynamic activity was less but still significantly increased when
participants had no task to keep them alert and attentive to the stimuli.
% we have no task neither
Our paradigm is similar in that sense that our participants had no behavioral or
cognitive task (e.g. forming a mental image of the stimuli; cf.
\citep{ocraven2000mental})  but just had to ``enjoy the audio-description''.
% but we are still different
Our paradigm still differs from \citep{epstein1998ppa} because the modeled
stimulus features were incidentally embedded in a continuous stream of auditory
information.
% concluding statement: kinda automatic process
The lack of a task suggests that verbal spatial information is processed in the
anterior PPA in an automatic fashion and does not necessarily rely on
deliberately paying attention to verbal spatial information.
%
Further, the incidental occurrence of modeled features prevents participants
from making assumptions about the investigated perceptual process by just being
exposed to the paradigm which mimics experiencing the world outside the lab more
closely.

@@

\todo[inline]{how to discuss Bland-Altman-Plots???}

\todo[inline]{dunno if this is meaningful: z-scores in the anterior part of
    PPA are higher in AD contrasts than in contrast of localizer}

@@

>>>>

\begin{table*}[h!]
\caption{Significant clusters (z-threshold Z>3.4; p<.05 cluster-corrected)
    of the primary $t$-contrast for the audio-visual movie comparing cuts to a
    setting that was not depicted before to a recurring setting
    (\texttt{vse\_new > vpe\_old}).
    Clusters sorted by voxel size.
    The first brain structure given contains the voxel with the maximum Z-Value,
    followed by brain structures from posterior to anterior, and partially
    covered areas (l. = left; r. = right; c. = cortex; g. = gyrus).}
\label{tab:res-av-group1}
\begin{tabular}{rrrrrrrrrp{3cm}}
\toprule
& & & \multicolumn{3}{r}{max location (MNI)} & \multicolumn{3}{r}{center of gravity (MNI)} &
\\ \cmidrule{4-6} \cmidrule{7-9}
voxels & $p_{corr.}$ & Z-max & x & y & z  & x & y & z & structure \\
\midrule
3003 & 0 & 5.31 & 22.5 & -45.5 & -12 & 4.53 & -63.3 & -3.72 & r. lingual g.; r.
cuneal c., intracalcarine c., bilaterally occipital fusiform g., precuneus,temporal fusiform c., posterior parahippocampal c.  \\
154 & 0.000000656 & 4.46 & -35 & -83 & 28 & -32.8 & -86.2 & 21.4 & l. superior lateral occipital c. \\
121 & 0.00000769 & 4.65 & 25 & -80.5 & 25.5 & 23.7 & -83.8 & 25.4 & r. superior lateral occipital cortex \\
\bottomrule
\end{tabular}
\end{table*}

@@

\todo[inline]{if we report procedure of Sengupta as detailed as it is now in the
following paragraph (imo it's too long), we probably need to explain the
differences between strict, relaxed, simple set in more detail in the method
section}
% Sengupta et al., 2016
The visual localizer experiment \citep{sengupta2016extension} yielded bilateral
[parahippocampal] clusters in 12 of 14 subjects and an unilateral right clusters
in two subjects (sub-04, sub-20).
% Sengupta: 1 of 3
Individual PPAs were assessed by visually inspecting thresholded $z$-maps
(Z>1.64, p<.05 cluster corrected) of three different $t$-contrasts
(\textit{strict}, \textit{relaxed}, and \textit{simple} stimulus set, cf.
\citep{sengupta2016extension}).
% procedure a)
Starting with the most conservative contrast (\textit{strict} set) and a
threshold of t = 2.5, we looked for clusters with at least 20 voxels (using
AFNI).
% procedure b)
We titrated [?] the threshold in the range of [2, 3] until we found an isolated
cluster for the PPA.
% Sengupta: procedure b)
If a cluster was not found or not isolated, we used a contrast from the
\textit{relaxed} set, or finally the \textit{simple} \todo{not used in any VP
for PPA}set, and repeated the process until we found a cluster that matched the
expected anatomical location based on literature \citep{epstein1998ppa}.

@@

\todo[inline]{BA-plots only shortly mentioned now}
% Bland-Altman-Plots
To better depict the agreement and difference between the results of the visual
localizer and the primary AD contrast, we created a Bland-Altman-Plot for every
subject (see ).
% what it depicts
Each subplot of Figure \ref{fig:bland-altman} visualizes the mean value and
difference (localizer minus AD) of two spatially corresponding voxels in the
unthresholded $z$-maps.
% top KDE plot
A shift of the distribution to voxels with a mean above zero can be seen the
further we constrain voxels to the individual PPA (see KDE plot for the x-axis).
% right KDE plot
Values above the horizontal line depict voxels that show a higher $z$-value in
the dedicated localizer, values below the horizontal line depict voxels that
show higher $z$-value in the AD stimulus.

@@

% previous studies
Previous studies reported bilaterally increased hemodynamic activity in the PPA
when participants were watching static pictures of landscape compared to
pictures of faces or objects (e.g. \citep{epstein1998ppa,
epstein1999parahippocampal}) whereas one study using spoken sentences reported
mixed results \citep{aziz2008modulation}.
% current study: similar
In line with previous studies, we use here also operationalize spatial
perception via general linear model (GLM) $t$-contrasts in two naturalistic
stimuli.
% current study: dissimilar
Contrary to previous studies, our current approach is not based on
carefully designed sets of stimuli but based on annotated stimulus features
incidentially occurring in an audio-visual movie and its audio-description.
% group AV
On a group level, whole brain-analysis results for the movie stimulus show
signifcantly increased hemodynamic activity spatially overlapping with a
traditionally localized PPA but also extending into earlier visual cortices.
% group AD
Results for the audio-description stimulus reveal significant activation
restricted to the anterior part of the PPA.
% individual level
On an individual level, results of the audio-description show significant
bilateral clusters in the anterior PPA of nine subjects and significant
unilateral clusters in two subjects.
% meaning 1
Results suggest that increased activation in the PPA during the perception of
static pictures generalizes to the perception of spatial information embedded in
a movie and an exclusively auditory stimulus.
% meaning 2
Our results provide further evidence that the PPA can be divided into functional
subregions. An auditory narrative might substitute a visual paradigm to localize
the PPAs anterior part in visually impaired subjects.

@@

% intro
First, we analyzed data from the movie stimulus offering ecologically more valid
but still visual stimulation.
%
An early study \citep{bartels2004mapping} that manually annotated the content
(color, faces, language, and human bodies) of movie frames found that
specialization of functional areas is preserved during movie watching.
%
Contrary to \citep{bartels2004mapping}, we categorized the frames after movie
cuts independent of the frames' content.\todo{PPA in
    \citep{hasson2004intersubject} but do reverse ISC}
% hypo
Despite this ``adventurous'' / ad hoc approach, we hypothesized that
[confounding variables could/would average out and] our whole-brain analyses
would lead to significant clusters in the PPA.
% results
Group results of the AV stimulus' primary contrast yielded a clusters that span
the group overlap of individual PPA ROIs from anterior to posterior.
% difference in location/size to AD and VIS
The cluster also extends into medial regions (dorsal precuneus and dorsal
posterior cingulate cortices), and into more posterior regions (occipital
fusiform gyrus and intracalcarine cortex) bilaterally.
% confound of higher perception
The larger extension into more posterior, primary visual areas can be attributed
to the fact that we averaged the content of individual frames after a cut and
did not control for confounding features like depicted faces or objects or
attentional focus of subjects.
%
\todo[inline]{bigger size of clusters is not surprising;  imo still impressive
low amount of random clusters in the brain (and not one third of brain
significant); Clusters in Bartels (2004) are actually kinda big, too;)}
%
Noteworthy, we here exploited a confound in the stimulus structure induced by
cinematographic tendencies (cf. method section;
% a)
a) movies tend to establish the setting and the spatial relationships within a
setting at the beginning of a movie;
% b)
b) the field sizes of movie shots tend to decrease when switching back to
already established settings
% c)
c) shots within a recurring locale or setting tend to shift to depicting persons
and objects \citep{brown2012cinematography, mercado2011filmmakers}.
% interpretation
-> concluding statement?
% shortcomings
Since the capability to isolate clusters or networks correlating with specific
perceptual (or cognitive) processes is influenced by the amount of annotated
stimulus features further studies focusing on visual perception should annotate
and model visual features of naturalistic stimuli more rigorously.
% solution
Future studies that aim to use a movie to localize different visual areas should
extensively annotate the content of frames (e.g. using the open-source solution
``Pliers'' for feature extraction from a visual naturalistic stimulus;
\citep{mcnamara2017developing}) and record the subject's visual attention via
eye-tracking.

\todo[inline]{Nevertheless: that this simple approach works actually suprisingly
well; shows that a lot of confounds average out, since we clusters are not super
big or all over the brain (and that across contrasts)}

\todo[inline]{on the other hand: movies are nice but have idiosyncrasies; so,
maybe you should be aware of these idiosyncrasies (and control for it) in case
you wanna use movies for research}

% summary: nevertheless
\todo[inline]{Summary: so, yes, what is the main message of this
``cross-modal-control-movie-thing''?? cf. intro: ``works'' but clusters more
widespread}

@@

@@

% intro
Second, we analyzed data from the audio-description.
% hypothesis
Encouraged by \citep{aziz2008modulation}, we also hypothesized that spatial
information embedded in an exclusively auditory stimulus would correlate with
increased hemodynamic activity in the PPA.
% results
Group results of the AD stimulus' primary contrast yielded spatially concise
clusters in the anterior part of the PPA group overlap that we gained from a
visual localizer experiment \citep{sengupta2016extension}.
% diff to Aziz (2008)
Unlike \citep{aziz2008modulation} who modeled events from on- to offset of
sentences (describing unknown and famous places and faces), we modeled events
from on- to offset of single words (that indicats the visual content to the
listener).
% conclusion
\citep{aziz2008modulation} found significantly increased activity in only the
left PPA and only for sentences describing famous places compared to famous
faces.\todo{averaged across voxels in PPA/FFA defined by localizer}
%
Contrary, our group results suggest that auditory spatial information
compared to non-spatial information correlates with bilaterally increased
activation in its anterior.\todo{any concluding statement?}

% previous studies: no task
Usually studies that use small sets of experimentally controlled stimuli also
employ a task to keep subjects attentive to the stimuli.
% but: Epstein (1998)
Nevertheless, one early block-design study \citep{epstein1998ppa} compared
results from a paradigm that employed a (perceptual) judgment task of static
pictures to the same paradigm but without that task.
% results during no task
Hemodynamic activity was less but still significantly increased when
participants had no task to keep them alert and attentive to the stimuli.
% we have no task neither
Our paradigm is similar in that sense that our participants had no behavioral or
cognitive task (e.g. forming a mental image of the stimuli; cf.
\citep{ocraven2000mental})  but just had to ``enjoy the audio-description''.
% but still: we are different
Our paradigm still differs from \citep{epstein1998ppa} because the modeled
stimulus features were incidentally embedded in a continuous stream of auditory
information preventing participants from making assumptions about the
investigated perceptual process.
% concluding statement: kinda automatic process
Hence, current results from our paradigm also suggest that verbal spatial
information is processed in the anterior PPA casually and does not [necessarily]
rely on [deliberately] paying attention to verbal spatial information.

@@

\todo[inline]{how to discuss Bland-Altman-Plots???; dunno if this is meaningful:
z-scores in the anterior part of PPA are higher in AD contrasts than in contrast
of localizer}

@@

%
Since the annotation of the narrator's voice allowed us to better/cleaner/nicer
operationalize spatial perception than the movie's annotation, we here
hypothesized
% AD stimulus
